Exploratory Plots

### 2020-06-20 exploratory/2020/README.Rmd
Update sensspec & benchmark boxplots with cowplot

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      message = FALSE,
                      fig.path = "figures/"
                      )
```
```{r lib}
library(here)
library(knitr)
library(tidyverse)
theme_set(theme_classic())
color_palette <- RColorBrewer::brewer.pal(4, "Dark2")
dataset_colors <- c(
  human = color_palette[[3]],
  marine = color_palette[[1]],
  mouse = color_palette[[4]],
  soil = color_palette[[2]]
)
```

# Fitting datasets to a reference database vs _de novo_ clustering
```{r functions}
relevel_method <- function(df) {
  df %>%
    mutate(method = fct_relevel(method, c("open", "closed", "de_novo")))
}
```

### Performance as measured by MCC
```{r fit_db_sensspec}
sensspec <-
  read_tsv(here('subworkflows/2_fit_reference_db/results/sensspec.tsv')) %>%
  relevel_method()
sensspec %>%
  group_by(dataset, method) %>%
  ggplot(aes(x = method, y = mcc, color = dataset)) +
  geom_boxplot(alpha = 0.5) +
  scale_color_manual(values = dataset_colors) +
  #ylim(0, 1) +
  facet_grid(dataset ~ ref)
```

### Performance as measured by runtime
```{r fit_db_benchmarks, warning=FALSE}
benchmarks <-
  read_tsv(here('subworkflows/2_fit_reference_db/results/benchmarks.tsv')) %>%
  relevel_method
benchmarks %>%
  group_by(dataset, method) %>%
  ggplot(aes(x = method, y = s, color = dataset)) +
  geom_boxplot() +
  scale_color_manual(values = dataset_colors) +  
  facet_wrap("ref") +
  labs(y = 'seconds')
```

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      message = FALSE,
                      fig.path = "figures/"
                      )
```
```{r lib}
library(cowplot)
library(here)
library(knitr)
library(tidyverse)
theme_set(theme_classic())
color_palette <- RColorBrewer::brewer.pal(4, "Dark2")
dataset_colors <- c(
  human = color_palette[[3]],
  marine = color_palette[[1]],
  mouse = color_palette[[4]],
  soil = color_palette[[2]]
)
```

# Fitting datasets to a reference database vs _de novo_ clustering
```{r functions}
relevel_method <- function(df) {
  df %>%
    mutate(method = fct_relevel(method, c("open", "closed", "de_novo")))
}
plot_box_mcc <- function(df) {
  df %>%
    group_by(dataset, method) %>%
    ggplot(aes(x = method, y = mcc, color = dataset)) +
    geom_boxplot(alpha = 0.5) +
    scale_color_manual(values = dataset_colors) +
    ylim(0.6, 1) +
    facet_grid(dataset ~ ref) +
    theme(legend.position = "None",
          axis.title.x = element_blank())
}
plot_box_time <- function(df) {
  df %>%
    group_by(dataset, method) %>%
    ggplot(aes(x = method, y = s, color = dataset)) +
    geom_boxplot() +
    scale_color_manual(values = dataset_colors) +
    ylim(0, 1000) +
    facet_wrap("ref") +
    labs(y = 'seconds') +
    theme(axis.title.x = element_blank())
}
```

### Performance as measured by MCC
```{r fit_db_sensspec}
sensspec_fit <-
  read_tsv(here('subworkflows/2_fit_reference_db/results/sensspec.tsv')) 
sensspec_clust <- read_tsv(here('subworkflows/1_prep_samples/results/sensspec.tsv'))
#sensspec <- bind_rows(sensspec_fit, sensspec_clust)

mcc_plot_fit <- sensspec_fit %>% 
  plot_box_mcc() +
  theme(axis.text.y = element_blank(),
        axis.title.y = element_blank())
mcc_plot_clust <- sensspec_clust %>% 
  plot_box_mcc() + 
  theme(strip.background.y = element_blank(),
        strip.text.y = element_blank())

plot_grid(mcc_plot_clust, mcc_plot_fit, 
          align = "h", rel_widths = c(1,3))
```

### Performance as measured by runtime
```{r fit_db_benchmarks, warning=FALSE}
benchmarks_fit <-
  read_tsv(here('subworkflows/2_fit_reference_db/results/benchmarks.tsv'))
benchmarks_clust <- read_tsv(here('subworkflows/1_prep_samples/results/benchmarks.tsv'))

time_plot_fit <- benchmarks_fit %>% 
  plot_box_time() +
  theme(axis.text.y = element_blank(),
        axis.title.y = element_blank())
time_plot_clust <- benchmarks_clust %>% 
  plot_box_time() +
  theme(legend.position = "None")

plot_grid(time_plot_clust, time_plot_fit,
          align = "h", rel_widths = c(1,3))
```
